---
title: "A general workflow"
author: "Alexis Gaevsky"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Starting out
Creating an object of parameters as as list


```{r}
scbParams <- list(tParCount = 10,
                  sampleSize = 10,
                  mean = 0,
                  sd = 1,
                  kernel = normalDifferenceKernel,
                  u = seq(-10, 10, 0.1),
                  lag = 2,
                  nonCoverageProbability = 0.05,
                  c_k = -1.978325,
                  phi_k_norm_diff = 0.4065,
                  alphaCount = 10,
                  replicationCount = 10,
                  superReplicationCount = 10,
                  bwidth = 1)


```

Calling functions
```{r}
library(SCB)
scbList <- doAll(scbParams = scbParams)

```

Let's take a look at what we got
```{r}
scbList
```
